---
title: Complexity Aversion Analysis (v1)
date: "`r Sys.Date()`"
author: "fredcallaway"
output:
  rmdformats::robobook:
    code_folding: hide
    self_contained: true
---

```{r, include=FALSE}
source('setup.r')
knitr::opts_chunk$set(
    fig.path="figs/",
    results='asis', warning=FALSE, message=FALSE, fig.width=4, fig.height=3, fig.align="center"
)
version = "v1"
load_data = function(name) read_csv(glue('../data/{version}/{name}.csv'))

choices = load_data('choices')
all_data = load_data('anonymized_raw')
lottery_values = load_data('lottery_values')

valuations = choices %>% 
    group_by(participant, question) %>% 
    filter(!choose_lottery) %>% 
    slice(1) %>% 
    ungroup() %>% 
    select(!choose_lottery) %>% 
    left_join(lottery_values)
```

## Attention check

```{r}
q1 = valuations %>% 
    filter(question == "Example") %>% 
    transmute(participant, first_guess=value)

q2 = valuations %>% 
    filter(question == "areyousure") %>% 
    transmute(participant, second_guess=value)

check = left_join(q1, q2) %>% 
    mutate(check=if_else(first_guess == 4, "first", if_else(second_guess == 4, "second", "failed")))

check %>% 
    count(check) %>% 
    kable
```

Guesses of people who failed:

```{r}
check %>% 
    filter(check == "failed") %>% 
    select(first_guess, second_guess) %>% 
    t %>% 
    kable(col.names=NULL)
```

For now, we are including everyone. It doesn't seem to make much difference.

## Critical trials

Our critical prediction is an interaction between complexity and the prior
on the value assigned to a lottery, with more preference (or less aversion)
for the complex lottery in the high prior condition. We do not see that. But
it is very noisy. Error bars are 95% CI. Dots are individuals.


```{r, fig.width=7, fig.height=3}
critical = valuations %>% 
    filter(grepl("7", question)) %>% 
    mutate(
        prior = if_else(str_detect(question, "'"), "high", "low"),
        complexity = str_match(question, "Q7'?(\\w+)")[,2]
    ) %>% 
    left_join(check) %>% 
    filter(check != "failed")

p1 = critical %>% 
    ggplot(aes(complexity, value, color=prior)) +
    stat_summary(fun.data=mean_cl_boot, position=position_dodge(width=.1)) +
    stat_summary(aes(group=prior), fun=mean, geom="line", position=position_dodge(width=.1))

p2 = critical %>% 
    ggplot(aes(complexity, value, color=prior)) +
    theme(legend.position="none") +
    geom_quasirandom(dodge.width=1, size=.5)

p1 + p2 + plot_layout(guides="collect")
```

```{r}
critical %>% 
    group_by(prior, complexity) %>% 
    summarise(across(value, list(mean=mean, sd=sd))) %>% 
    kable(digits=3)
```

## Prior-building trials

In these plots, each line is a participant. Relative value normalizes
the provided value such that 0 is the minimum possible, 1 is the maximum,
and 0.5 is the risk-neutral normative response. You can better see
that there is some stability in risk preferences there.

```{r, fig.width=7, fig.height=6}

relative_score = function(x, lo, hi) {
    ((x - lo) / (hi - lo))
    # (((x - lo) / (hi - lo)) - 0.5) * 2
}

X = valuations %>% 
    filter(str_detect(question, 'Q[1-6]')) %>% 
    group_by(participant) %>% filter(n() == 6) %>% 
    mutate(rel_value = relative_score(value, heads, tails)) %>% 
    mutate(trial = str_sub(question, 2, 2)) %>% 
    mutate(prior = if_else(str_detect(question, "'"), "high", "low"))

# ht = X %>% distinct(prior, trial, heads, tails)

p1 = X %>% 
    ggplot(aes(trial, value, group=participant, color=prior)) +
    geom_line(alpha=0.3, size=.5) +
    # geom_line(aes(trial, heads,group=0), ht) +
    # geom_line(aes(trial, tails,group=0), ht) +
    facet_wrap(~prior) + theme(legend.position="none")

p2 = X %>% 
    ggplot(aes(fct_reorder(participant, rel_value), rel_value, color=prior)) +
    geom_point(alpha=0.5) +
    facet_wrap(~prior) + 
    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
    labs(y="relative value", x="participant")

(p1 / p2) + plot_layout(heights=c(1,2))
```

## Thoughts on complex trials

```{r}
all_data %>% 
    left_join(select(critical, participant, complexity)) %>% 
    filter(complexity == "complex") %>% 
    select(Q48) %>% 
    drop_na(Q48) %>% 
    kable
```
